An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-30 paper/paper.tex
Paper: Some fixes.

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they backup. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation through the use of file transfer parallelization.
\end{abstract}

@@

As the capacity and performance of hard drives continue to increase over time, users continue to store their data in greater volumes. This includes high resolution photos, videos, and audio for the personal user, and databases, source code repositories, and operating system images for the technical user. The increase in stored data gives rise to a greater need for the data to be backed up, in preparation for the undesirable event that one's hard drive becomes inaccessible. This can happen if one's computer crashes, the hard drive fails, or the computer is lost or stolen.

>>>>

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they back up. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation through the use of file transfer parallelization.
\end{abstract}

@@

As the capacity and performance of hard drives continues to increase over time, users continue to store their data in greater volumes. This includes high resolution photos, videos, and audio for the personal user, and databases, source code repositories, and operating system images for the technical user. The increase in stored data gives rise to a greater need for the data to be backed up, in preparation for the undesirable event that one's hard drive becomes inaccessible. This can happen if one's computer crashes, the hard drive fails, or the computer is lost or stolen.
